### 2018-04-15 tex/paper.tex
added Haskell code for the step function to the paper

\item \haskellinline{Null} is the null contract; it will always be quiescent.

\item \haskellinline{CommitCash idCC p v t1 t2 k1 k2}  For this contract to make progress,\begin{itemize}
\item either before the timeout \haskellinline{t1} the user \haskellinline{p} makes a cash commitment of value 
\haskellinline{v} and timeout \haskellinline{t2}  with the identifier \haskellinline{idCC}, 
\item
or the timeout \haskellinline{t1} is exceed.
\end{itemize} 
In the first case, a \haskellinline{SuccessfulCommit} action is generated and the contract continues as 
\haskellinline{k1}; in the second case no action is generated and the contract continues as 
\haskellinline{k2}. While neither case holds the contract is quiescent, waiting for the cash to be committed.

@@

\item \haskellinline{RedeemCC idCC k} (\haskellinline{CC} stands for cash commitment.) For this contract to make progress, the creator of the cash commitment with identifier \haskellinline{idCC} is required to redeem the unspent funds in that commitment; the contract then continues as \haskellinline{k}, and the action \haskellinline{CommitRedeemed} is produced. 
Committed cash can only be redeemed once, and an attempt to redeem it a second time will produce a  \haskellinline{DuplicateRedeem} action, continuing as \haskellinline{k}.

@@

\item \haskellinline{Pay p1 p2 v t k} makes it possible, assuming that sufficient funds are available, for 
\haskellinline{p1} to claim  a payment of \haskellinline{v} from \haskellinline{p2} before the timeout 
\haskellinline{t}. The contract continues as \haskellinline{k}. By `available' we mean that sufficient commitments have 
been made and  not yet expired to cover the payment; in this case the payment  uses the currency allocated by the cash 
commitments made by \haskellinline{p1} that expire the earliest.

@@

\item \haskellinline{Both k1 k2} enforces the behaviour of both contracts \haskellinline{k1} and \haskellinline{k2}. Because the model is stateful and produces output actions, to make a step it is necessary to execute a single step of each of  the contracts \haskellinline{k1} and \haskellinline{k2} in sequence: first \haskellinline{k1} then \haskellinline{k2}.

@@

\item \haskellinline{When obs timeout k def_k} This contract will not progress until \haskellinline{obs} is \haskellinline{True} or until the current block number is greater than or equal to the one specified by timeout. In case the timeout applies, the contract will continue as \haskellinline{def_k}, if the timeout does not apply and \haskellinline{obs} is \haskellinline{True}, then the contract continues as \haskellinline{k}. Otherwise the contract is quiescent.
\end{itemize}
We look next at an example of Marlowe in action.

>>>>

\item \haskellinline{Null} is the null contract; it will always be quiescent:

\smallskip
\begin{haskellcode}
step _ st Null _ = (st, Null, [])
\end{haskellcode}
\smallskip

\item \haskellinline{CommitCash idCC p v t1 t2 k1 k2}  For this contract to make progress,\begin{itemize}
\item either before the timeout \haskellinline{t1} the user \haskellinline{p} makes a cash commitment of value 
\haskellinline{v} and timeout \haskellinline{t2}  with the identifier \haskellinline{idCC}, 
\item
or the timeout \haskellinline{t1} is exceed:
\end{itemize}

\smallskip
\begin{haskellcode}
step 
  commits 
  st 
  c@(CommitCash ident person val start_timeout end_timeout con1 con2) 
  os
  | cexe || cexs = (st {sc = ust}, con2, [])
  | Set.member (CC ident person cval end_timeout) (cc commits)
        = (st {sc = ust}, con1, [SuccessfulCommit ident person cval])
  | otherwise = (st, c, [])
  where ccs = sc st
        cexs = expired (blockNumber os) start_timeout
        cexe = expired (blockNumber os) end_timeout
        cns = (person, if cexe || cexs 
                          then ManuallyRedeemed 
                          else NotRedeemed cval end_timeout)
        ust = Map.insert ident cns ccs
        cval = evalMoney st val
\end{haskellcode}
\smallskip
In the first case, a \haskellinline{SuccessfulCommit} action is generated and the contract continues as 
\haskellinline{k1}; in the second case no action is generated and the contract continues as 
\haskellinline{k2}. While neither case holds the contract is quiescent, waiting for the cash to be committed.

@@

\item \haskellinline{RedeemCC idCC k} (\haskellinline{CC} stands for cash commitment.) For this contract to make progress, the creator of the cash commitment with identifier \haskellinline{idCC} is required to redeem the unspent funds in that commitment; the contract then continues as \haskellinline{k}, and the action \haskellinline{CommitRedeemed} is produced.

\smallskip
\begin{haskellcode}
step commits st c@(RedeemCC ident con) _ =
    case Map.lookup ident ccs of
      Just (person, NotRedeemed val _) ->
        let newstate = 
                st {sc = Map.insert ident (person, ManuallyRedeemed) ccs} in
        if Set.member (RC ident person val) (rc commits)
        then (newstate, con, [CommitRedeemed ident person val])
        else (st, c, [])
      Just (person, ManuallyRedeemed) ->
        (st, con, [DuplicateRedeem ident person])
      Nothing -> (st,c,[])
    where
        ccs = sc st
\end{haskellcode}
\smallskip

Committed cash can only be redeemed once, and an attempt to redeem it a second time will produce a  \haskellinline{DuplicateRedeem} action, continuing as \haskellinline{k}.

@@

\item \haskellinline{Pay p1 p2 v t k} makes it possible, assuming that sufficient funds are available, for 
\haskellinline{p1} to claim  a payment of \haskellinline{v} from \haskellinline{p2} before the timeout 
\haskellinline{t}. The contract continues as \haskellinline{k}.

\smallskip
\begin{haskellcode}
step inp st c@(Pay idpay from to val expi con) os
  | expired (blockNumber os) expi = (st, con, [ExpiredPay idpay from to cval])
  | right_claim =
    if committed st from bn >= cval
      then (newstate, con, [SuccessfulPay idpay from to cval])
      else (st, con, [FailedPay idpay from to cval])
  | otherwise = (st, c, [])
  where
    cval = evalMoney st val
    newstate = stateUpdate st from to bn cval
    bn = blockNumber os
    right_claim =
      case Map.lookup (idpay, to) (rp inp) of
        Just claimed_val -> claimed_val == cval
        Nothing -> False
\end{haskellcode}
\smallskip

By `available' we mean that sufficient commitments have 
been made and  not yet expired to cover the payment; in this case the payment  uses the currency allocated by the cash 
commitments made by \haskellinline{p1} that expire the earliest.

@@

\item \haskellinline{Both k1 k2} enforces the behaviour of both contracts \haskellinline{k1} and \haskellinline{k2}.

\smallskip
\begin{haskellcode}
step comms st (Both con1 con2) os =
    (st2, result, ac1 ++ ac2)
    where
        result | res1 == Null = res2
               | res2 == Null = res1
               | otherwise = Both res1 res2
        (st1,res1,ac1) = step comms st con1 os
        (st2,res2,ac2) = step comms st1 con2 os
\end{haskellcode}
\smallskip

Because the model is stateful and produces output actions, to make a step it is necessary to execute a single step of each of  the contracts \haskellinline{k1} and \haskellinline{k2} in sequence: first \haskellinline{k1} then \haskellinline{k2}.

@@

\smallskip
\begin{haskellcode}
step _ st (Choice obs conT conF) os =
    if interpretObs st obs os
        then (st,conT,[])
        else (st,conF,[])
\end{haskellcode}
\smallskip

\item \haskellinline{When obs timeout k def_k} This contract will not progress until \haskellinline{obs} is \haskellinline{True} or until the current block number is greater than or equal to the one specified by timeout. In case the timeout applies, the contract will continue as \haskellinline{def_k}, if the timeout does not apply and \haskellinline{obs} is \haskellinline{True}, then the contract continues as \haskellinline{k}. Otherwise the contract is quiescent.

\smallskip
\begin{haskellcode}
step _ st (When obs expi con con2) os
  | expired (blockNumber os) expi = (st,con2,[])
  | interpretObs st obs os = (st,con,[])
  | otherwise = (st, When obs expi con con2, [])
  \end{haskellcode}
\smallskip

\end{itemize}
We look next at an example of Marlowe in action.
